\textbf{Code exploration}

### 2024-11-03 paper_Roychoudhury_code.Rnw
Update paper_Roychoudhury_code.Rnw

\documentclass[a4paper, 11pt]{article}
\usepackage[margin=0.9in]{geometry}
\usepackage{amsmath, amssymb} % math
\usepackage[round]{natbib} % bibliography
\usepackage[dvipsnames,table]{xcolor} % colors
\usepackage[onehalfspacing]{setspace} % more space
\usepackage{graphicx}
\usepackage{float}

@@

\subsection{Reproduce Figure 1}
In Figure 1, the two plots illustrate the operating characteristics of dual-criterion designs with 309 and 420 events. The number 309 is the minimum sample size calcualted under the example conditions $\sigma=2$, $\alpha=2.5\%$, log hazard ratios NV = $\log(1)$, DV = $\log(0.8)$.
\begin{equation*}
n_{min}=\frac{2^2 \times z_{0.025}^2}{(\log{1}-\log{0.8})^2} = 308.594 \approx 309
\end{equation*}
The probability of making a ``GO'' decision is the probability of the estimate smaller than the decision value and 
<<Figure 1, eval=FALSE, echo=TRUE, results=hide, fig=TRUE, highlight=TRUE>>=
# a sequence of true hazard ratios in log scale.
t.d <- log(seq(0.5, 1, 0.01))

# Left panel: sample size = 309
n <- 309
sd <- sqrt((2^2)/n) #sigma assumed to be 2. 
cut.ssig <- log(0.8) # statistical significance 
cut.crel <- log(0.8) # clinical relevance DV=0.8
pp.go <- pnorm(cut.crel, t.d, sd)
pp.ngo <- 1- pnorm(cut.ssig, t.d, sd)
pp.intd <- 1 -pp.go - pp.ngo

# Right panel: sample size = 420 
n <- 420
sd <- sqrt((2^2)/n) #sigma assumed to be 2
#cut.ssig <- log(0.83) # statistical significance NV=1????
cut.ssig <- log(1-qnorm(0.975)*sqrt(2^2/420))
cut.crel <- log(0.8) # critical relevance
pp.go6 <- pnorm(cut.crel, t.d, sd)
pp.ngo6 <- 1- pnorm(cut.ssig, t.d, sd)
pp.intd6 <- 1 -pp.go6 - pp.ngo6

#png("Figure 1.png", width = 1200, height = 800, res = 150)
par(mfrow=c(1,2),las=1)
plot(exp(t.d), pp.go, type="l", xlab= "Hazard Ratio", ylab="Probability", 
     main="n=309", col="green", ylim=c(0,1),xlim=c(0.5,1))
lines(exp(t.d), pp.ngo, type="l", col="red")
lines(exp(t.d), pp.intd, type="l", col="darkgoldenrod1")
abline(v=0.8, lty=1)

plot(exp(t.d), pp.go6, type="l", xlab= "Hazard Ratio", ylab="Probability", 
     main="n=420", col="green", ylim=c(0,1),xlim=c(0.5,1))
lines(exp(t.d), pp.ngo6, type="l", col="red")
lines(exp(t.d), pp.intd6, type="l", col="darkgoldenrod1")
abline(v=0.8, lty=1)
@

<<Figure 1, fig=TRUE>>=
# Load necessary libraries
library(ggplot2)
library(cowplot)

# Data preparation
t.d <- log(seq(0.5, 1, 0.01))

# Left panel data (n = 309)
n1 <- 309
sd1 <- sqrt((2^2) / n1)  # sigma assumed to be 2
cut.ssig1 <- log(0.8)    # statistical significance 
cut.crel1 <- log(0.8)    # clinical relevance DV=0.8
pp.go1 <- pnorm(cut.crel1, t.d, sd1)
pp.ngo1 <- 1 - pnorm(cut.ssig1, t.d, sd1)
pp.intd1 <- 1 - pp.go1 - pp.ngo1

# Right panel data (n = 420)
n2 <- 420
sd2 <- sqrt((2^2) / n2)  # sigma assumed to be 2
cut.ssig2 <- log(1 - qnorm(0.975) * sqrt(2^2 / 420)) # statistical significance 
cut.crel2 <- log(0.8)  # clinical relevance
pp.go2 <- pnorm(cut.crel2, t.d, sd2)
pp.ngo2 <- 1 - pnorm(cut.ssig2, t.d, sd2)
pp.intd2 <- 1 - pp.go2 - pp.ngo2

# Data for plotting
df1 <- data.frame(HazardRatio = exp(t.d), GO = pp.go1, NOGO = pp.ngo1, 
                  Inconclusive = pp.intd1)
df2 <- data.frame(HazardRatio = exp(t.d), GO = pp.go2, NOGO = pp.ngo2, 
                  Inconclusive = pp.intd2)

# Left panel plot (n = 309)
p1 <- ggplot(df1, aes(x = HazardRatio)) +
  geom_line(aes(y = GO, color = "GO")) +
  geom_line(aes(y = NOGO, color = "NOGO")) +
  geom_line(aes(y = Inconclusive, color = "Inconclusive")) +
  geom_vline(xintercept = c(0.8, 1.0), linetype = "dashed", color = "black") +  
  labs(x = "Hazard Ratio", y = "Probability", title = "n = 309") +
  scale_color_manual(values = c("GO" = "green", "NOGO" = "red", 
                                "Inconclusive" = "darkgoldenrod1")) +
  theme_minimal() +
  theme(legend.position = "bottom")

# Right panel plot (n = 420)
p2 <- ggplot(df2, aes(x = HazardRatio)) +
  geom_line(aes(y = GO, color = "GO")) +
  geom_line(aes(y = NOGO, color = "NOGO")) +
  geom_line(aes(y = Inconclusive, color = "Inconclusive")) +
  geom_vline(xintercept = c(0.8, 1.0), linetype = "dashed", color = "black") +
  labs(x = "Hazard Ratio", y = "Probability", title = "n = 420") +
  scale_color_manual(values = c("GO" = "green", "NOGO" = "red", 
                                "Inconclusive" = "darkgoldenrod1")) +
  theme_minimal() +
  theme(legend.position = "bottom")

# Combine the plots with shared legend at the bottom
combined_plot <- plot_grid(p1 + theme(legend.position = "none"),
                           p2 + theme(legend.position = "none"),
                           ncol = 2,
                           align = 'hv',
                           rel_widths = c(1.5, 1.5))  
# Adjust widths to make the plots wider

# Extract legend from one of the plots
legend <- get_legend(p1)

# Final plot with shared legend at the bottom
final_plot <- plot_grid(combined_plot, legend, ncol = 1, rel_heights = c(1, 0.1))
print(final_plot)
@

\section{Example 1: A randomized PoC design with time-to-event data}
Randomized, double-blind, RCT. Patients were randomized equally to: (experimental drug + standard care) OR (standard care only).\\
Primary outcome of interest (or called ``endpoint'') is the progression-free survival (PFS), which is the time when the disease or cancer do not get worse. The endpoint was assessed with a \emph{log-rank test} and \emph{Cox regression} with treatment as a covariate.
\begin{itemize}
\item \emph{log-rank test}: compare the survival distributions of two or more groups. It tests the hypothesis that there is no difference in survival (or time-to-event) between the two groups. If the log-rank test indicates a significant difference, it suggests the treatment affects how long patients live without their disease worsening.
\item \emph{Cox regression}: estimate the hazard ratio between two groups, which tells us the relative risk of disease progression in the treatment group compared to the control group. If the $\text{HR} < 1$, it suggests that the new treatment delays disease progression better than the control treatment.
\end{itemize}
As for the DV, HR=0.7 was deemed necessary to be clinically meaningful. Values larger than 0.7 are unsatisfactory to clearly justify further development of the drug.\\
So the dual-criterion is:
\begin{enumerate}
\item Statistical significance: one-sided p-value of log-rank test $\leq 0.1$.
\item Clinical relevance: estimated HR from Cox regression $\leq 0.70$.
\end{enumerate}
\subsection{Reproduce Table 3}
Attempt to reproduce the values in Table 3. The main problem is to find the correct value for $\sigma$. There seem to be no detailed information about the choice of value for $\sigma$. We chose it to be 2 according to page 455 in the paper. However, under this value, the calculated values do not agree with the ones in Table 3. \\
Also, the calculation of $\hat{\theta} = 0.736, 0.708, 0.659, 0.761$ should be looked into when the correct $\sigma$ is decided. The current understanding is that these values are calculated when the estimate $\hat{\theta} > \text{DV}$ and the confidence interval just touches 1, i.e. NO-GO is implied.
<< echo = TRUE >>=
n.min <- (4*qnorm(0.9)^2)/(log(1)-log(0.7))^2

@@

# Dual-criterion design: alpha=0.1, DV=0.7, n=70
n1 <- 70
sd1 <- sqrt((2^2)/n1) #sigma assumed to be 2?
#sqrt((1.723522^2)/n1)
cut.ssig <- log(0.736) # statistical significance NV=1
cut.crel <- log(0.7) # critical relevance
pp.go1 <- pnorm(cut.crel, t.d, sd1)
pp.ngo1 <- 1- pnorm(cut.ssig, t.d, sd1)
pp.intd1 <- 1 -pp.go1 - pp.ngo1

subtable1 <- matrix(data=c(t.d, pp.go1,pp.ngo1,pp.intd1), ncol=4)

@@

subtable2 <- matrix(data=c(t.d, pp.go2,pp.ngo2,pp.intd2), ncol=4)

# Dual-criterion design: alpha=0.1, beta=0.1, n=55
n3 <- 55
sd3 <- sqrt((2*2^2)/n3)
cut.ssig <- qnorm(0.9, 0.5, sd3) # different from 0.708
cut.crel <- qnorm(0.9, 0.5, sd3)
pp.go3 <- pnorm(cut.crel, t.d, sd3)
pp.ngo3 <- 1-pnorm(cut.ssig, t.d, sd3)
pp.intd3 <- 1 -pp.go3 - pp.ngo3

subtable3 <- matrix(data=c(t.d, pp.go3,pp.ngo3,pp.intd3), ncol=4)

# Dual-criterion design: alpha=0.1, beta=0.2, n=38
n4 <- 38
sd4 <- sqrt((2*2^2)/n4)
cut.ssig <- qnorm(0.8, 0.5, sd4) # different from 0.659
cut.crel <- qnorm(0.8, 0.5, sd4)
pp.go4 <- pnorm(cut.crel, t.d, sd4)
pp.ngo4 <- 1-pnorm(cut.ssig, t.d, sd4)
pp.intd4 <- 1 -pp.go4 - pp.ngo4

subtable4 <- matrix(data=c(t.d, pp.go4,pp.ngo4,pp.intd4), ncol=4)

# Dual-criterion design: alpha=0.2, beta=0.1, n=38
n5 <- 38
sd5 <- sqrt((2*2^2)/n5)
cut.ssig <- qnorm(0.9, 0.5, sd5) # different from 0.659
cut.crel <- qnorm(0.9, 0.5, sd5)
pp.go5 <- pnorm(cut.crel, t.d, sd5)
pp.ngo5 <- 1-pnorm(cut.ssig, t.d, sd4)
pp.intd5 <- 1 -pp.go5 - pp.ngo5

subtable5 <- matrix(data=c(t.d, pp.go5,pp.ngo5,pp.intd5), ncol=4)

# Table3 <- rbind(subtable1[6:11,],subtable2[6:11,],subtable3[6:11,], 
# subtable4[6:11,], subtable5[6:11,])
# colnames(Table3) <- c("True HR", "GO", "NO-GO", "Inconclusive")
# rownames(Table3) <- c(rep("1",6),rep("2",6),rep("3",6),rep("4",6),rep("5",6))
# Table3
@

<<plots, echo = FALSE>>=

#Plot

plot(t.d, pp.go1, type="l", xlab= "Hazard Ratio", ylab="Probability", 
     main="n=70", col="green", ylim=c(0,1))
lines(t.d, pp.ngo1, type="l", col="red")
lines(t.d, pp.intd1, type="l", col="darkgoldenrod1")
abline(h=0.1, lty=2)
abline(h=0.8, lty=2)
abline(v=0.8, lty=1)

plot(t.d, pp.go2, type="l", xlab= "Hazard Ratio", ylab="Probability", 
     main="n=52", col="green", ylim=c(0,1))
lines(t.d, pp.ngo2, type="l", col="red")
lines(t.d, pp.intd2, type="l", col="darkgoldenrod1")
abline(h=0.1, lty=2)
abline(h=0.8, lty=2)
abline(v=0.8, lty=1)

\section{Example 2: A single-arm PoC design with binary data}
Experimental drug in Chinese patients with non-small-cell lung cancer. \\
Primary endpoint is objective response rate (ORR), which quantifies the preliminary efficacy of the experimental drug. \\
Prior: minimally informative unimodal beta prior distribution $Beta(0.0811,1)$, which has mean 0.75.\\
NV is set to 7.5\% rather than 0, because of the absence of a comparator (in single arm trials). \\
DV is set to be 10\%+7.5\%=17.5\%.\\
So the dual-criterion is:
\begin{enumerate}
\item Bayesian statistical significance: $\mathbb{P}(ORR \geq 7.5\% | data) \geq 0.95$
\item Clinical relevance: Posterior median $\geq 17.5\%$
\end{enumerate}
The minimal sample size was 22. Final sample size 25. \\
Null hypothesis: there is no effect of the drug, i.e. ORR=7.5\%\\
$\mathbb{P}(\text{type I error})=\mathbb{P}(\text{reject } H_0 | H_0 \text{ is true})=\mathbb{P}(\text{reject } H_0 | ORR \leq 7.5\%)$\\
$\mathbb{P}(\text{type II error})=\mathbb{P}(\text{not reject } H_0 | H_0 \text{ is false})=\mathbb{P}(\text{reject } H_0 | ORR= \text{response rate})$\\
Table 4 results show that this dual-criterion design is a three-outcome design with desirable properties.

>>>>

\documentclass[a4paper, 11pt]{article}
\usepackage[margin=0.9in]{geometry}
\usepackage{amsmath, amssymb} % math
\usepackage[round]{natbib} % bibliography
\usepackage[dvipsnames,table]{xcolor} % colors
\usepackage[onehalfspacing]{setspace} % more space
\usepackage{graphicx}
\usepackage{float}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}

@@

\subsection{Reproduce Figure 1}
In Figure 1, the two plots illustrate the operating characteristics of dual-criterion designs with 309 and 420 events. The number 309 is the minimum sample size calcualted under the example conditions $\sigma=2$, $\alpha=2.5\%$, log hazard ratios NV = $\log(1)$, DV = $\log(0.8)$.
\begin{equation*}
n_{min}=\frac{2^2 \times z_{0.025}^2}{(\log{1}-\log{0.8})^2} = 308.594 \approx 309
\end{equation*}
The probability of making a ``GO'' decision is the probability of the estimate smaller than the decision value and 
\begin{center}
<<Figure 1, fig=TRUE, results=hide>>=
# Load necessary libraries
library(ggplot2)
library(cowplot)
library(gridExtra)
library(grid)

# Sequence of true hazard ratios in log scale
t.d <- log(seq(0.5, 1, 0.01))

# Left panel (n = 309)
n1 <- 309
sd1 <- sqrt((2^2) / n1)
cut.ssig1 <- log(0.8)
cut.crel1 <- log(0.8)
pp.go1 <- pnorm(cut.crel1, t.d, sd1)
pp.ngo1 <- 1 - pnorm(cut.ssig1, t.d, sd1)
pp.intd1 <- 1 - pp.go1 - pp.ngo1
df1 <- data.frame(HazardRatio = exp(t.d), GO = pp.go1, NOGO = pp.ngo1, Inconclusive = pp.intd1)

# Right panel (n = 420)
n2 <- 420
sd2 <- sqrt((2^2) / n2)
cut.ssig2 <- log(1) - qnorm(0.975) * sqrt(2^2 / 420)
cut.crel2 <- log(0.8)
pp.go2 <- pnorm(cut.crel2, t.d, sd2)
pp.ngo2 <- 1 - pnorm(cut.ssig2, t.d, sd2)
pp.intd2 <- 1 - pp.go2 - pp.ngo2
df2 <- data.frame(HazardRatio = exp(t.d), GO = pp.go2, NOGO = pp.ngo2, Inconclusive = pp.intd2)

# Define the line colors and types
line_colors <- c("GO" = "green3", "Inconclusive" = "darkgoldenrod2", "NO-GO" = "red3")
line_types <- c("GO" = "solid", "Inconclusive" = "dotted", "NO-GO" = "dashed")

# Plot for n = 309
p1 <- ggplot(df1, aes(x = HazardRatio)) +
  geom_line(aes(y = GO, color = "GO", linetype = "GO"),size=0.8) +
  geom_line(aes(y = NOGO, color = "NO-GO", linetype = "NO-GO"),size=0.8) +
  geom_line(aes(y = Inconclusive, color = "Inconclusive", 
                linetype = "Inconclusive"),size=1.5) +
  geom_vline(xintercept = c(0.8, 1.0), linetype = "dashed", color = "black") +
  labs(title = "Nevent = 309") +
  scale_color_manual(values = line_colors) +
  scale_linetype_manual(values = line_types) +
  theme_minimal() +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5, face = "bold"),
    panel.grid.minor = element_blank(),
    axis.title.y = element_blank(),  # Remove individual y-labels
    axis.title.x = element_blank()
  )

# Plot for n = 420
p2 <- ggplot(df2, aes(x = HazardRatio)) +
  geom_line(aes(y = GO, color = "GO", linetype = "GO"),size=0.8) +
  geom_line(aes(y = NOGO, color = "NO-GO", linetype = "NO-GO"),size=0.8) +
  geom_line(aes(y = Inconclusive, color = "Inconclusive", 
                linetype = "Inconclusive"),size=1.5) +
  geom_vline(xintercept = c(0.8, 1.0), linetype = "dashed", color = "black") +
  labs(title = "Nevent = 420") +
  scale_color_manual(values = line_colors) +
  scale_linetype_manual(values = line_types) +
  theme_minimal() +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5, face = "bold"),
    panel.grid.minor = element_blank(),
    axis.title.y = element_blank(),  # Remove individual y-labels
    axis.title.x = element_blank()
  )

# Combine the plots into a single figure without individual y-axis labels
combined_plots <- plot_grid(p1, p2, ncol = 2, align = 'hv', rel_widths = c(1, 1))

# Extract and create a shared legend
legend <- get_legend(
  p1 + theme(legend.position = "right") +
    guides(color = guide_legend(title = "Decision", nrow = 1), 
           linetype = guide_legend(title = "Decision", nrow = 1)))

# Add a shared y-axis label using grid.arrange
final_plot <- grid.arrange(
  arrangeGrob(combined_plots, 
              left = textGrob("Probability", rot = 90, vjust = 1.2),
              bottom = textGrob("Hazard Ratio",just = "centre")),
  legend = legend,
  ncol = 1,
  heights = c(10, 1) 
)

# Print the final plot
print(final_plot)
@
\end{center}

\section{Example 1: A randomized PoC design with time-to-event data}
Randomized, double-blind, RCT. Patients were randomized equally to: (experimental drug + standard care) OR (standard care only).\\
Primary outcome of interest (or called ``endpoint'') is the progression-free survival (PFS), which is the time when the disease or cancer do not get worse. The endpoint was assessed with a \emph{log-rank test} and \emph{Cox regression} with treatment as a covariate.
\begin{itemize}
\item \emph{log-rank test}: compare the survival distributions of two or more groups. It tests the hypothesis that there is no difference in survival (or time-to-event) between the two groups. If the log-rank test indicates a significant difference, it suggests the treatment affects how long patients live without their disease worsening.
\item \emph{Cox regression}: estimate the hazard ratio between two groups, which tells us the relative risk of disease progression in the treatment group compared to the control group. If the $\text{HR} < 1$, it suggests that the new treatment delays disease progression better than the control treatment.
\end{itemize}
As for the DV, HR=0.7 was deemed necessary to be clinically meaningful. Values larger than 0.7 are unsatisfactory to clearly justify further development of the drug.\\
So the dual-criterion is:
\begin{enumerate}
\item Statistical significance: one-sided p-value of log-rank test $\leq 0.1$.
\item Clinical relevance: estimated HR from Cox regression $\leq 0.70$.
\end{enumerate}
\subsection{Reproduce Table 3}
Attempt to reproduce the values in Table 3. The main problem is to find the correct value for $\sigma$. There seem to be no detailed information about the choice of value for $\sigma$. We chose it to be 2 according to page 455 in the paper. \\
Also, the calculation of $\hat{\theta} = 0.736, 0.708, 0.659, 0.761$ should be looked into when the correct $\sigma$ is decided. The current understanding is that these values are calculated when the estimate $\hat{\theta} > \text{DV}$ and the confidence interval just touches 1, i.e. NO-GO is implied.
<< Table 3, echo = TRUE, results=tex >>=
library(kableExtra)
n.min <- (4*qnorm(0.9)^2)/(log(1)-log(0.7))^2

@@

# Dual-criterion design: alpha=0.1, DV=0.7, n=70
n1 <- 70
sd1 <- sqrt((2^2)/n1) #sigma assumed to be 2?
#sqrt((1.723522^2)/n1)
# cut.ssig <- 0-qnorm(0.9)* sqrt(2^2 / 70)
cut.ssig <- log(exp(0-qnorm(0.9)* sqrt(2^2 / n1))) # statistical significance NV=1
cut.crel <- log(0.7) # critical relevance
pp.go1 <- pnorm(cut.crel, t.d, sd1)
pp.ngo1 <- 1- pnorm(cut.ssig, t.d, sd1)
pp.intd1 <- 1 -pp.go1 - pp.ngo1

subtable1 <- matrix(data=round(c(exp(t.d), pp.go1,pp.ngo1,pp.intd1),3), ncol=4)

@@

subtable2 <- matrix(data=round(c(exp(t.d), pp.go2,pp.ngo2,pp.intd2),3), ncol=4)

# Dual-criterion design: alpha=0.1, beta=0.1, n=55
n3 <- 55
sd3 <- sqrt((2^2)/n3)
cut.ssig <- log(0.708)
cut.crel <- log(0.708)
cut.ssig <- qnorm(0.9,log(0.5),sd3) # different from 0.708
cut.crel <- qnorm(0.9,log(0.5),sd3)
pp.go3 <- pnorm(cut.crel, t.d, sd3)
pp.ngo3 <- 1-pnorm(cut.ssig, t.d, sd3)
pp.intd3 <- 1 -pp.go3 - pp.ngo3

subtable3 <- matrix(data=round(c(exp(t.d), pp.go3,pp.ngo3,pp.intd3),3), ncol=4)

# Dual-criterion design: alpha=0.1, beta=0.2, n=38
n4 <- 38
sd4 <- sqrt((2^2)/n4)
cut.ssig <- log(exp(0-qnorm(0.9)* sqrt(2^2 / n4))) # different from 0.659
cut.crel <- log(exp(0-qnorm(0.9)* sqrt(2^2 / n4)))
pp.go4 <- pnorm(cut.crel, t.d, sd4)
pp.ngo4 <- 1-pnorm(cut.ssig, t.d, sd4)
pp.intd4 <- 1 -pp.go4 - pp.ngo4

subtable4 <- matrix(data=round(c(exp(t.d), pp.go4,pp.ngo4,pp.intd4),3), ncol=4)

# Dual-criterion design: alpha=0.2, beta=0.1, n=38
n5 <- 38
sd5 <- sqrt((2^2)/n5)
cut.ssig <- log(exp(0-qnorm(0.8)* sqrt(2^2 / n5))) 
# How is the power guaranteed to be 0.1? This is only using alpha=0.2.
cut.crel <- log(exp(0-qnorm(0.8)* sqrt(2^2 / n5)))
pp.go5 <- pnorm(cut.crel, t.d, sd5)
pp.ngo5 <- 1-pnorm(cut.ssig, t.d, sd5)
pp.intd5 <- 1 -pp.go5 - pp.ngo5

subtable5 <- matrix(data=round(c(exp(t.d), pp.go5,pp.ngo5,pp.intd5),3), ncol=4)

# Combine subtables by rows
combined_table <- rbind(subtable1, subtable2, subtable3, subtable4, subtable5)

# Convert to data frame for better kable support
combined_table <- as.data.frame(combined_table)

kable(combined_table, format = "latex", align = "c", booktabs = TRUE,
      col.names = c("True HR", "GO", "NO-GO", "Inconclusive")) %>%
  kable_styling(full_width = FALSE, position = "center",
                latex_options = c("hold_position","scale_down")) %>%
  add_header_above(c("Reproduced Table 3" = 4)) %>%
  group_rows("Subtable 1", 1, 6) %>%
  group_rows("Subtable 2", 7, 12) %>%
  group_rows("Subtable 3", 13, 18) %>%
  group_rows("Subtable 4", 19, 24) %>%
  group_rows("Subtable 5", 25, 30)
@

\pagebreak
\section{Example 2: A single-arm PoC design with binary data}
Experimental drug in Chinese patients with non-small-cell lung cancer. \\
Primary endpoint is objective response rate (ORR), which quantifies the preliminary efficacy of the experimental drug. \\
Prior: minimally informative unimodal beta prior distribution $Beta(0.0811,1)$, which has mean 0.75.\\
NV is set to 7.5\% rather than 0, because of the absence of a comparator (in single arm trials). \\
DV is set to be 10\%+7.5\%=17.5\%.\\
So the dual-criterion is:
\begin{enumerate}
\item Bayesian statistical significance: $\mathbb{P}(ORR \geq 7.5\% | data) \geq 0.95$
\item Clinical relevance: Posterior median $\geq 17.5\%$
\end{enumerate}
The minimal sample size was 22. Final sample size 25. \\
Null hypothesis: there is no effect of the drug, i.e. ORR=7.5\%\\
$\mathbb{P}(\text{type I error})=\mathbb{P}(\text{reject } H_0 | H_0 \text{ is true})=\mathbb{P}(\text{reject } H_0 | ORR \leq 7.5\%)$\\
$\mathbb{P}(\text{type II error})=\mathbb{P}(\text{not reject } H_0 | H_0 \text{ is false})=\mathbb{P}(\text{reject } H_0 | ORR= \text{response rate})$\\
Table 4 results show that this dual-criterion design is a three-outcome design with desirable properties.
